---
title: "DATA 607 Assignment 2"
author: Leslie Tavarez
output: html_document
date: "2024-09-16"
---
# Connect to a MySQL Database
```{r}
#libraries
library(RMySQL)
library(RMariaDB)
library(DBI)
library(tidyverse)


#database connection 
con <- dbConnect(RMySQL::MySQL(),
                 dbname = "leslie.tavarez85",
                 host = "cunydata607sql.mysql.database.azure.com",
                 user = "leslie.tavarez85",
                 password = "a2c0b934dba8a1ef")


#query data from pupularmovies table
query <- "SELECT * FROM `leslie.tavarez85`.`pupularmovies`;"
pupularmovies <- dbGetQuery(con, query)

#show the imported dataframe from MySQL
print(pupularmovies)

#close connection when done 
dbDisconnect(con)
```

#Part 4: Missing data strategy 
There are a few ways to handle missing data but I do not want to imput a zero for NA values, replace it with the mean or make up information. Instead, I will just use the information that I have and analysis that data instead. I will do this by creating new tables for each movie omitting the NA/null values.

```{r}
#Let's use a visual to show our missing data 
library(mice)
md.pattern(pupularmovies)
```

#First, I need to transpose my data (flip rows and columns)
```{R}
movieRatings <- data.frame(t(pupularmovies[-1]))
colnames(movieRatings) <- pupularmovies[, 1]

print(movieRatings)

```
#Find mean of each movie omitting null values
```{R}
mean(movieRatings$Barbie, na.rm = TRUE)
mean(movieRatings$`BadBoys:RideOrDie`, na.rm = TRUE)
mean(movieRatings$`StarWars:TheLastJedi`, na.rm = TRUE)
mean(movieRatings$`AQuietPlace:DayOne`, na.rm = TRUE)
mean(movieRatings$FordvsFerrari, na.rm = TRUE)
mean(movieRatings$DunePtII, na.rm = TRUE)


```
Ford vs. Ferrari had the highest average rating of 4.5/5. Bad Boys and Star Wars are tied for second best with the same average rating of 3.5/5. A Quiet Place scored lower than I thought it would (I watched it in theaters and loved it). It averaged at a 3.3/5. 

In conclusion, I enjoyed using data I was able to obtain from students and fellow teachers. I did not use a software to gather information since I wanted it to be more interactive but I normally have my students use smartsheet, google or survey monkey to make surveys! 

Standariziation may increase the reliabilty and the consistency of surveys. I think it makes it easier to compare results. But, as a teacher who has taken way too many surveys, sometimes I think it may result in response bias and it is difficult to capture complex information. Respondents may not be able to explain their thoughts or experience with a simple rating scale. While doing this lab, I was able to hear their perspective on each movie and their reason why they voted the way they did. If I were to standardize the rating for this lab specifically, I can have people rate from 1-5 to the nearest integer instead of accepting decimal values. 